network_analysis

### 2020-09-09 analyses/beta_diversity_v2.Rmd
update

### betaboot function: This bootstraps the partitioning of interaction beta-diversity to account for differences in the number of sampling dates for each site in the same way the my other bootstrapping function ("bootnet" or something like that) bootstraps the calculation of network metrics. Note that due to some annoying behavior by webs2array(), I have to define an object within the for loop  of my function using the <<- global assignment operator. This is bad coding, but I can't figure out another way to get webs2array() to find the object it needs to find.
```{r message=FALSE}
betaboot <- function(x, n, iter) {

  out <- data.frame()

  index <- 0

  t_filter <- x %>%
    dplyr::select(site, date, year) %>%
    unique() %>%
    group_by(site, year) %>%
    mutate(transects = n()) %>%
    filter(transects >= n)

  for(i in 1:iter){

    index <- index + 1

    net.sub <- x %>%
      semi_join(t_filter) %>%
      ungroup() %>%
      dplyr::select(site, dayofyear) %>%
      unique() %>%
      group_by(site) %>%
      sample_n(n) %>%
      left_join(x)

    web <<- net.sub %>%
      group_by(site, bb.sp, plant.sp) %>%
      summarize(freq = n()) %>%
      dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
      data.frame() %>% # convert to data frame
      frame2webs() # convert to to bipartite web

    array <- webs2array(web)

    beta <- betalinkr_multi(array, partition.st = TRUE, partition.rr = TRUE, binary = TRUE) %>%
      as_tibble() %>%
      mutate(iteration = rep(index, n()))

    out <- bind_rows(out, beta)
  }

  out <- out %>%
    as_tibble() %>%
    dplyr::select(site1 = i, site2 = j, everything()) %>%
    gather(metric, value, -c(site1, site2, iteration)) %>%
    mutate(metric.class = case_when(
        metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
        metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
        metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
        metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
      ),
      iteration = factor(iteration))
}
```

### Tabulate webs
S	= beta_S, the dissimilarity in species composition
OS = beta_OS, the dissimilarity (component) explained by "rewiring" among shared species
WN = beta_WN, the dissimilarity between the two networks
ST = beta_ST, the dissimilarity (component) explained by difference in species community composition 
```{r message=FALSE}
net2010 <- filter(net, year == 2010)
net2011 <- filter(net, year == 2011)
net2012 <- filter(net, year == 2012)

beta_2010 <- betaboot(net2010, 5, 50) %>%
  group_by(site1, site2, metric, metric.class) %>%
  summarize(value = mean(value)) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
         elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         ),
         year = factor(rep("2010", n())))

beta_2011 <- betaboot(net2011, 5, 50) %>%
  group_by(site1, site2, metric, metric.class) %>%
  summarize(value = mean(value)) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
         elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         ),
         year = factor(rep("2011", n())))

beta_2012 <- betaboot(net2012, 9, 50) %>%
  group_by(site1, site2, metric, metric.class) %>%
  summarize(value = mean(value)) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, site2, metric, metric.class, value, 
         elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         ),
         year = factor(rep("2012", n())))

beta_agg <- bind_rows(beta_2010, beta_2011, beta_2012)

#write_csv(beta_agg, "./output/aggregated_beta_diversity.csv")
#beta_agg <- read_csv("./output/aggregated_beta_diversity.csv")
```

### Plot results. There's nothing a Mantel test can tell me that I don't already know from the combination of plotting and GDM analysis.
```{r}
### Elevation
ggplot(filter(beta, year == "2010" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.45) +
  geom_smooth(method = "lm", formula =  y ~ poly(x, 3)) +
  facet_wrap(~metric.class) +
  theme_abyss()

ggplot(filter(beta, year == "2011" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.45) +
  geom_smooth(method = "lm", formula =  y ~ poly(x, 3)) +
  facet_wrap(~metric.class) +
  theme_abyss()

ggplot(filter(beta, year == "2012" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.45) +
  geom_smooth(method = "lm", formula =  y ~ poly(x, 3)) +
  facet_wrap(~metric.class) +
  theme_abyss()

ggplot(filter(beta, 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.45) +
  geom_smooth(method = "lm", formula =  y ~ poly(x, 3)) +
  facet_wrap(~metric.class) +
  theme_gray()

### Management
ggplot(filter(beta, year == "2010" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(man.diff, value)) +
  geom_boxplot() +
  facet_wrap(~metric, scales = "free") +
  theme_gray()

ggplot(filter(beta, year == "2011" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(man.diff, value)) +
  geom_boxplot() +
  facet_wrap(~metric, scales = "free") +
  theme_gray()

ggplot(filter(beta, year == "2012" & 
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(man.diff, value)) +
  geom_boxplot() +
  facet_wrap(~metric, scales = "free") +
  theme_gray()
```

@@

### Call gdm()
gdm_survey.2012 <- gdm(survey_sitepair.2012, geo = TRUE)
gdm.varImp(survey_sitepair.2012, geo = TRUE)

@@

### Call gdm()
gdm_survey.2011 <- gdm(survey_sitepair.2011, geo = TRUE)
#gdm.varImp(survey_sitepair, geo = TRUE)

summary(gdm_survey.2011)
plot(gdm_survey.2011)
#plotUncertainty(survey_sitepair, sampleSites = 0.7, bsIters = 50, geo  = TRUE)

@@

### Call gdm()
gdm_survey.2010 <- gdm(survey_sitepair.2010, geo = TRUE)
#gdm.varImp(survey_sitepair, geo = TRUE)

summary(gdm_survey.2010)
plot(gdm_survey.2010)
#plotUncertainty(survey_sitepair, sampleSites = 0.7, bsIters = 50, geo  = TRUE)
```

@@

### Call gdm()
gdm_bb.2010 <- gdm(bb_sitepair.2010, geo = TRUE)
gdm.varImp(bb_sitepair.2010, geo = TRUE)

@@

### Now let's look at interaction beta diversity. I don't think p-values would add anything to the interpretation I get from the plotted uncertainty, so it's okay that I can't get gdm.varImp() to work.
```{r}
### 2010
sitepair_2010 <- beta_2010 %>%
  ungroup() %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev.mean = elev1, s2.elev.mean = elev2) %>%
  data.frame()

gdm_2010 <- gdm(sitepair_2010, geo = TRUE)
gdm.varImp(sitepair_2010, geo = TRUE)

summary(gdm_2010)
plot(gdm_2010)
plotUncertainty(sitepair_2010, sampleSites = 0.7, bsIters = 50, geo  = TRUE)

### 2011
sitepair_2011 <- beta_2011 %>%
  ungroup() %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev.mean = elev1, s2.elev.mean = elev2) %>%
  data.frame()

gdm_2011 <- gdm(sitepair_2011, geo = TRUE)
gdm.varImp(sitepair_2011, geo = TRUE)

summary(gdm_2011)
plot(gdm_2011)
plotUncertainty(sitepair_2011, sampleSites = 0.7, bsIters = 50, geo  = TRUE)

### 2012
sitepair_2012 <- beta_2012 %>%
  ungroup() %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev.mean = elev1, s2.elev.mean = elev2) %>%
  data.frame()

gdm_2012 <- gdm(sitepair_2012, geo = TRUE)
gdm.varImp(sitepair_2012, geo = TRUE)

summary(gdm_2012)
plot(gdm_2012)
plotUncertainty(sitepair_2012, sampleSites = 0.7, bsIters = 50, geo  = TRUE)
```

### Transect-level analysis
```{r}
beta_site.date.2010 <- betalinkr_multi(array_site.date.2010, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE) %>%
  as_tibble() %>%
  separate(i, into = c("site1", "year1", "yday1"), sep = "_") %>%
  separate(j, into = c("site2", "year2", "yday2"), sep = "_") %>%
  left_join(site_data, by = c("site1" = "site"))%>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

### Plot transect-level analysis
```{r}
### Elevation diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Elevation diff within 1 wk time diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_abyss()

>>>>

### Tabulate webs
S	= beta_S, the dissimilarity in species composition
OS = beta_OS, the dissimilarity (component) explained by "rewiring" among shared species
WN = beta_WN, the dissimilarity between the two networks
ST = beta_ST, the dissimilarity (component) explained by difference in species community composition 
```{r message=FALSE}
net2010 <- filter(net, year == 2010) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

net2011 <- filter(net, year == 2011) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

net2012 <- filter(net, year == 2012) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

array_site.date.2010 <- webs2array(net2010) # convert to array of webs
array_site.date.2011 <- webs2array(net2011) # convert to array of webs
array_site.date.2012 <- webs2array(net2012) # convert to array of webs

beta_site.date.2010 <- betalinkr_multi(array_site.date.2010, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE) %>%
  as_tibble() %>%
  separate(i, into = c("site1", "year1", "yday1"), sep = "_") %>%
  separate(j, into = c("site2", "year2", "yday2"), sep = "_") %>%
  left_join(site_data, by = c("site1" = "site"))%>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

### Plot results. There's nothing a Mantel test can tell me that I don't already know from the combination of plotting and GDM analysis.
```{r}
### Elevation diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Elevation diff within 1 wk time diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_light()

### GDM analysis. I don't think p-values would add anything to the interpretation I get from the plotted uncertainty, so it's okay that I can't get gdm.varImp() to work.
```{r}
### 2010
sitepair_2010.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2010) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

gdm_WN.2010 <- gdm(sitepair_2010.WN, geo = TRUE)
gdm_WN.2010.imp <- gdm.varImp(sitepair_2010.WN, geo = TRUE)

summary(gdm_WN.2010)
plot(gdm_WN.2010)
plotUncertainty(sitepair_2010.WN, sampleSites = 0.7, bsIters = 10, geo  = TRUE)

### 2011
sitepair_2011.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2011) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

gdm_WN.2011 <- gdm(sitepair_2011.WN, geo = TRUE)
gdm_WN.2011.imp <- gdm.varImp(sitepair_2011.WN, geo = TRUE)

summary(gdm_WN.2011)
plot(gdm_WN.2011)
plotUncertainty(sitepair_2011.WN, sampleSites = 0.7, bsIters = 10, geo  = TRUE)

### 2012
sitepair_2012.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2012) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

gdm_WN.2012 <- gdm(sitepair_2012.WN, geo = TRUE)
gdm_WN.2012.imp <- gdm.varImp(sitepair_2012.WN, geo = TRUE)

summary(gdm_WN.2012)
plot(gdm_WN.2012)
plotUncertainty(sitepair_2012.WN, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
```

@@

### Call gdm()
gdm_survey.2012 <- gdm(survey_sitepair.2012, geo = TRUE)
gdm_survey.2012.imp <- gdm.varImp(survey_sitepair.2012, geo = TRUE)

@@

### Call gdm()
gdm_survey.2011 <- gdm(survey_sitepair.2011, geo = TRUE)
gdm_survey.2011.imp <- gdm.varImp(survey_sitepair.2011, geo = TRUE)

summary(gdm_survey.2011)
plot(gdm_survey.2011)
plotUncertainty(survey_sitepair, sampleSites = 0.7, bsIters = 50, geo  = TRUE)

@@

### Call gdm()
gdm_survey.2010 <- gdm(survey_sitepair.2010, geo = TRUE)
gdm_survey.2010.imp <- gdm.varImp(survey_sitepair.2010, geo = TRUE)

summary(gdm_survey.2010)
plot(gdm_survey.2010)
plotUncertainty(survey_sitepair, sampleSites = 0.7, bsIters = 50, geo  = TRUE)
```

@@

### Call gdm()
gdm_bb.2010 <- gdm(bb_sitepair.2010, geo = TRUE)
gdm_bb.2010.imp <- gdm.varImp(bb_sitepair.2010, geo = TRUE)

@@

### 2020-09-09 analyses/network_analysis.Rmd
update

### Can we make an argument for salvaging individual years, or parts of year?
#### 2011
ggplot(filter(samples, year == 2011), aes(elev.mean, obs)) +
  geom_point() +
  geom_smooth()
```

@@

# What about I? Does it do any better than S?
gam_d.sp_I <- gam(d ~ year + 
                     s(site, bs = "re") +
                     management +
                     s(bb.sp, bs = "re") +
                     s(elev.mean, by = bb.sp, bs = "tp", k = 8) +
                     s(fl.rich, k = 8) +
                     s(log.fl.abund, k = 8) +
                     s(log.bb.sp.abund, k = 5),
                   select = TRUE,
                   data = spmet,
                   method = "REML") %>% getViz()

>>>>

### Can we make an argument for salvaging individual years, or parts of year?
#### 2011
ggplot(filter(samples, year == 2011), aes(elev.mean, obs)) +
  geom_point() +
  geom_smooth()

### How evenly is the presence of species distributed across samples
bb_abund_sp <- net %>%
  group_by(site, dayofyear, elev.mean, year, bb.sp) %>%
  summarize(abund = n())

ggplot(filter(bb_abund_sp, year == 2011), aes(dayofyear, elev.mean)) +
  geom_point(aes(alpha = abund)) +
  facet_wrap(~bb.sp)
```

@@

# What about I? Does it do any better than S?
gam_d.sp_I <- gam(d ~ year + 
                     #s(site, bs = "re") +
                     management +
                     s(bb.sp, bs = "re") +
                     s(elev.mean, by = bb.sp, bs = "tp", k = 8) +
                     s(fl.rich, k = 8) +
                     s(log.fl.abund, k = 8) +
                     s(bb.sp.abund, k = 5),
                   select = TRUE,
                   data = spmet,
                   method = "REML") %>% getViz()
